---
title: "Homework 1"
author: Chariz Seijo
output: github_document
---

Solution to HW 1. 

```{r}
library(tidyverse)
```


# Problem 1

Create a data frame with the specified elements.

```{r create_df}
prob1_df =
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_vec = factor(c("low", "low", "low", "mod", "mod", "mod", "mod", "high", "high", "high"))
  )
```

Take the mean of each variable in my data frame.

```{r mean_pull_var}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

I can take the mean of numbers and logical but not character or factor.

```{r try_numeric}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```

I cannot convert the character variable, which helps explain why I cannot take the mean.

```{r}
as.numeric(pull(prob1_df, samp_gt_0)) * as.numeric(pull(prob1_df, samp))
as.numeric(as.factor(pull(prob1_df, samp_gt_0))) * as.numeric(pull(prob1_df, samp))
```


# Problem 2

Load penguins dataset.

```{r load_peng}
data("penguins", package = "palmerpenguins")
```

**This dataset contains `r nrow(penguins)` penguins and `r ncol(penguins)` variables: `r names(penguins)`. The mean of the flipper length is `r mean(pull(penguins))`.**

##### Scatter Plot of Penguin Flipper Length (mm) vs. Bill Length (mm)

```{r ggplot_peng}
ggplot(data = penguins, mapping = aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
ggsave("hw1plot.png")
```

